---
title: "PSTAT231-HW1"
author: "Eleanor Li"
date: "2022-10-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercise 1 
```{r}
library(ggplot2)
library(tidyverse)
data('mpg')
hist(mpg$hwy,main='Highway miles per gallon',xlab='Hmy')
```
# Most of the vehicles have the miles per gallon of 25-30 (around 80) on highway, secondly 15-20 mpg (70+) and thirdly 20-25 mpg (around 40). Fewer vehicles have the miles per gallon exceed 30 (20+) or less than 15 (less than 20).


# Exercise 2
```{r}
plot2 <- ggplot(mpg,aes(hwy,cty)) + 
  geom_point(color = 'red',size = 2)
print(plot2)
```
# There is a linear relation between hwy and cty that cty increases as hwy increases. It means that in this dataset, if miles per gallon is high on highway, it is likely to be be high in city as well and vice versa.


# Exercise 3 
```{r}
library(ggplot2)
ggplot(mpg,aes(y=forcats::fct_infreq(manufacturer)))+geom_bar()
```
# From the plot we can see that dodge produces the most cars and lincoln produced the least.


# Exercise 4
```{r}
boxplot(hwy ~ cyl,data=mpg)
```
# The pattern follows that as cyl increases, hwy decreases.


# Exercise 5 
```{r}
library(corrplot)
M = ggplot2::mpg %>% select_if(is.numeric) %>% cor(.)
corrplot(M,method='number', order='alphabet', type = 'lower')
```
# The displ and cyl or year; hwy and cty; year and cyl are positively related. The displ or cyl and cty; hwy and cyl or displ are negatively related. It is suprised that the year and the hwy has zero relation. Other relations make sense according to the ealier plot we make based on hwy and cty.

# Exercise 6
```{r}
library(ggthemes)
ggplot(mpg,aes(hwy,class))+
  geom_boxplot(color='black')+geom_point(position='jitter',color = 'grey')+theme_bw()+
  labs(x = 'Highway MPG', y = 'Vehicle Class')
```

# Exercise 7
```{r}
ggplot(mpg,aes(x=class,y=hwy,fill=factor(drv)))+geom_boxplot()
```

# Exercise 8
```{r}
library(ggthemes)
ggplot(mpg,aes(x=displ,y=hwy))+geom_point(aes(color=drv))+geom_smooth(formula = y~x, method = 'loess', aes(linetype = drv), se = FALSE)
```